---
title: 'Homework 4: Bags, Forests, Boosts, oh my'
author: "Eric Stromgren"
date: "2/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libs, message = F, warning = F, include = F}
library(tidyverse)
library(broom)
library(glmnet)
library(caret)
library(ISLR)
library(janitor)
library(stringr)
library(rpart)
library(rpart.plot)
library(partykit)
library(randomForest)
library(MASS)
library(gbm)
theme_set(theme_bw())
```


## Problem 1

Problem 7 from Chapter 8 in the text. To be specific, please use a sequence of
`ntree` from 25 to 500 in steps of 25 and `mtry` from 3 to 9 for by 1. 

## Answer 1
```{r}
set.seed(1234)
df <- tbl_df(Boston)
inTraining <- createDataPartition(df$medv, p = .75, list = F)
training <- df[inTraining, ]
testing  <- df[-inTraining, ]
```


## Problem 2

Problem 8 from Chapter 8 in the text. Set your seed with 9823 and split into 
train/test using 50\% of your data in each split. In addition to 
parts (a) - (e), do the following:

1. Fit a gradient-boosted tree to the training data and report the estimated 
test MSE. 
2. Fit a multiple regression model to the training data and report the 
estimated test MSE
3. Summarize your results. 
